---
title: CrossTalkeR - Installation and Basic Execution
author:
- name: James S. Nagai
  affiliation: Institute for Computational Genomics,
               Faculty of Medicine,
               RWTH Aachen University,
               Aachen, 52074 Germany
- name: Nils B. Leimkühler
  affiliation: Department of Hematology and Stem Cell Transplantation,
               University Hospital Essen,
               Germany
- name: Vanessa Klöker
  affiliation: Institute for Computational Genomics,
               Faculty of Medicine,
               RWTH Aachen University,
               Aachen, 52074 Germany
- name: Michael T. Schaub
  affiliation:
     - Department of Computer Science,
       RWTH Aachen University,
       Aachen, Germany
- name: Rebekka K. Schneider
  affiliation:
    - Department of Hematology,
      Erasmus Medical Center,
      Rotterdam, 3015GD,
      the Netherlands
    - Department of Cell Biology,
      Institute for Biomedical Engineering,
      Faculty of Medicine,
      RWTH Aachen University,
      Aachen, 52074 Germany
    - Oncode Institute,
      Erasmus Medical Center,
      Rotterdam, 3015GD,
      the Netherlands
- name: Ivan G. Costa
  affiliation:
     - Institute for Computational Genomics,
       Faculty of Medicine,
       RWTH Aachen University,
       Aachen, 52074 Germany
output:
     html_document
vignette: |
      %\VignetteIndexEntry{CrossTalkeR-HumanMyfib}
      %\VignetteEngine{knitr::rmarkdown}
      %\VignetteEncoding{UTF-8}
---
# CrossTalkeR - Installation and Basic Execution

Here we like to give a short introduction on the installation and the basic usage of CrossTalkeR.

## Install

You can install and load the CrossTalkeR package with the simple commands below:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("https://github.com/CostaLab/CrossTalkeR", build_vignettes = TRUE)
require(CrossTalkeR)
```

There are the following possible system dependencies:
```{r, eval = FALSE}
libudunits2-dev
libgdal-dev
gdal-bin
libproj-dev
proj-data
proj-bin
libgeos-dev
```

## Basic Execution
Here we show the most basic way to execute CrossTalkeR. All you need to provide are the paths to the ligand-receptor interaction analysis results and a path to save the results to:
```{r, eval = FALSE}
library(CrossTalkeR)

paths <- c('Condition1' = "/path/to/condition1/LR-interactions.csv",
           'Condition2' = "/path/to/condition2/LR-interactions.csv")

output <- "/path/to/output/folder/"
data <- generate_report(paths,
                out_path=output,
                out_file = 'vignettes_example.html',
                output_fmt = "html_document",
                report = TRUE,
                org = "hsa")

```


It is also possible to just perform the analysis part of CrossTalker, without generating the report:
```{r, eval = FALSE}
library(CrossTalkeR)

paths <- c('Condition1' = "/path/to/condition1/LR-interactions.csv",
           'Condition2' = "/path/to/condition2/LR-interactions.csv")

output <- "/path/to/output/folder/"
data <- analise_LR(paths,
                out_path=output,
                org = "hsa")

```

A second possibility is to generate the reports from existing CrossTalkeR objects. In this case the out_path should point to the folder with the 'LR_data_final.Rds' file.
```{r, eval = FALSE}
library(CrossTalkeR)

output <- "/path/to/output/folder/"
data <- make_report(out_path=output,
                out_file = 'vignettes_example.html',
                output_fmt = "html_document",
                report = TRUE,
                org = "hsa")

```

