---
title: CrossTalkeR - Basic Usage
author:
- name: James S. Nagai
  affiliation: Institute for Computational Genomics,
               Faculty of Medicine,
               RWTH Aachen University,
               Aachen, 52074 Germany
- name: Nils B. Leimkühler
  affiliation: Department of Hematology and Stem Cell Transplantation,
               University Hospital Essen,
               Germany
- name: Vanessa Klöker
  affiliation: Institute for Computational Genomics,
               Faculty of Medicine,
               RWTH Aachen University,
               Aachen, 52074 Germany
- name: Michael T. Schaub
  affiliation:
     - Department of Computer Science,
       RWTH Aachen University,
       Aachen, Germany
- name: Rebekka K. Schneider
  affiliation:
    - Department of Hematology,
      Erasmus Medical Center,
      Rotterdam, 3015GD,
      the Netherlands
    - Department of Cell Biology,
      Institute for Biomedical Engineering,
      Faculty of Medicine,
      RWTH Aachen University,
      Aachen, 52074 Germany
    - Oncode Institute,
      Erasmus Medical Center,
      Rotterdam, 3015GD,
      the Netherlands
- name: Ivan G. Costa
  affiliation:
     - Institute for Computational Genomics,
       Faculty of Medicine,
       RWTH Aachen University,
       Aachen, 52074 Germany
output:
     html_document
vignette: |
      %\VignetteIndexEntry{CrossTalkeR-install-basicusage}
      %\VignetteEngine{knitr::rmarkdown}
      %\VignetteEncoding{UTF-8}
---
# CrossTalkeR - Basic Execution

Here we like to give a short introduction on the basic usage of CrossTalkeR.


## Basic Execution
Here we show the most basic way to execute CrossTalkeR. All you need to provide are the paths to the ligand-receptor interaction analysis results and a path to save the results to:

```{r, eval = FALSE}
library(CrossTalkeR)

paths <- c('Condition1' = "/path/to/condition1/LR-interactions.csv",
           'Condition2' = "/path/to/condition2/LR-interactions.csv")

output <- "/path/to/output/folder/"
data <- generate_report(paths,
                out_path=output,
                out_file = 'vignettes_example.html',
                output_fmt = "html_document",
                report = TRUE,
                org = "hsa", 
                filtered_net=TRUE)

```

In case the **tables are already obtained inside your R session**, one can use the following approach(This also apply for the functions below).

```{r, eval = FALSE}
obj1 <- "a condition1 data frame object"
obj2 <- "a condition2 data frame object"

paths <- list('Condition1' = obj1,
           'Condition2' = obj2)

output <- "/path/to/output/folder/"
data <- generate_report(paths,
                out_path=output,
                out_file = 'vignettes_example.html',
                output_fmt = "html_document",
                report = TRUE,
                org = "hsa", 
                filtered_net=TRUE)

```

## Performing only the analysis

To just **perform the analysis** part of CrossTalker, **without generating the report**:
```{r, eval = FALSE}
library(CrossTalkeR)

paths <- c('Condition1' = "/path/to/condition1/LR-interactions.csv",
           'Condition2' = "/path/to/condition2/LR-interactions.csv")

output <- "/path/to/output/folder/"
data <- analise_LR(paths,
                out_path=output,
                org = "hsa" 
                filtered_net=TRUE)

```
## Getting Report from an existing project

An addictional possibility is to **generate the reports from existing CrossTalkeR objects**. In this case the out_path should point to the folder with the 'LR_data_final.Rds' file.
```{r, eval = FALSE}
library(CrossTalkeR)

output <- "/path/to/output/folder/"
data <- make_report(out_path=output,
                out_file = 'vignettes_example.html',
                output_fmt = "html_document",
                report = TRUE,
                org = "hsa" 
                filtered_net=TRUE)

```

