---
title: "Report diferential analysis"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
html_document:
toc: yes
toc_depth: 3
theme: simplex

params:

  obj1: "path to obj"
  obj2: "target gene"
  obj3: "target tf-gene"
  thr: 'percentage edges to plot'

---

```{r message=FALSE, warning=FALSE, echo=FALSE, include=FALSE, echo=FALSE}
require(igraph)
require(dplyr)
require(tibble)
require(tidyr)
require(patchwork)
require(stringr)
require(CrossTalkeR)
require(ggraph)
require(graphlayouts)
require(pals)
require(factoextra)
require("DT")
require(ComplexHeatmap)
require(ggrepel)
require(knitr)
require(extrafont)
extrafont::loadfonts()

if(is.null(params$obj3)){
  tfFlag <- FALSE
}else {
  tfFlag <- TRUE
}



```



### PCA GCI

*Here, a Principal Component Analysis (PCA) was done using the cell-gene interaction topological measures. High ranked observations $(>=2\sigma^{2})$ are labeled and each measure contribution is placed in the coordinate system.*

#### PCA GCI All Genes

```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=10,fig.height=5}
path <- params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
p1 <- plot_pca_LR_comparative(all_data,dims=c(1,2),ret=T,ggi=TRUE,include_tf=tfFlag)
p2 <- plot_pca_LR_comparative(all_data,dims=c(3,4),ret=T,ggi=TRUE,include_tf=tfFlag)
print(p1+p2 )

```



```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=10,fig.height=5, eval = tfFlag}
asis_output("#### PCA GCI Ligand and Receptor Genes\\n")
path <- params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
p1 <- plot_pca_LR_comparative(all_data,dims=c(1,2),ret=T,ggi=TRUE,include_tf=tfFlag,gene_types = "LR")
p2 <- plot_pca_LR_comparative(all_data,dims=c(3,4),ret=T,ggi=TRUE,include_tf=tfFlag,gene_types = "LR")
print(p1+p2)

```





```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=10,fig.height=5, eval = tfFlag}
asis_output("#### PCA GCI Transcription Factor Genes\\n")
path <- params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)

p1 <- plot_pca_LR_comparative(all_data,dims=c(1,2),ret=T,ggi=TRUE,include_tf=tfFlag,gene_types = "TF")
p2 <- plot_pca_LR_comparative(all_data,dims=c(3,4),ret=T,ggi=TRUE,include_tf=tfFlag,gene_types = "TF")
print(p1+p2    )

```


### Pagerank Log Ratio


```{r fig.align='center',warning=FALSE,echo=FALSE,eval=TRUE}
all_data <- readRDS(path)
for (i in 2:length(names(all_data@rankings))) {
  curr <- names(all_data@rankings)[i]
  if (str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, 'ggi', negate = FALSE)) {
    tmp <- top_n(all_data@rankings[[curr]], 20, abs(.data$Pagerank))
    signal <- ifelse(tmp$Pagerank < 0, 'negative', 'positive')
    print(ggplot(tmp, aes(x = Pagerank, y = reorder(nodes, Pagerank), fill = signal)) +
            geom_bar(stat = "identity") +
            scale_fill_manual(values = c(Blue2DarkOrange18Steps[4], Blue2DarkOrange18Steps[14])) +
            theme_minimal())
  }
}
```





### PCA GCI Table

```{r fig.align='center',warning=FALSE,echo=FALSE}
out <- c()
out1 <- list()
all_data <- readRDS(path)
for (i in 1:length(names(all_data@pca))) {
  curr <- names(all_data@pca)[i]
  if (str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)) {
    rmd_title <- paste0(curr, '_tbl')
    rmd_title1 <- paste0(curr, '_pca')
    title <- paste0('\n\n#### Table PCA CGI ', curr)
    knit_expanded <- paste0("```{r , results='", rmd_title, "', echo=FALSE, warning=FALSE}\n\n
         pca <- all_data@pca[['", curr, "']]$x[,1:2]
         pca[,1] <- round(pca[,1],6)
         pca[,2] <- round(pca[,2],6)
         ranking <- cbind(all_data@rankings[['", curr, "']][,2:dim(all_data@rankings[['", curr, "']])[2]],pca[all_data@rankings[['", curr, "']]$nodes,])
         datatable(ranking,
                 caption='", curr, "',
                 extensions = 'Buttons',
                 options = list(dom = 'Bfrtip',
                                buttons = c('copy',
                                            'csv',
                                            'excel',
                                            'pdf', 'print'),
                               autoWidth = FALSE
                               ))\n\n```")
    out <- c(out, knit_expanded)
    out1[[curr]] <- knit_expanded
  }

}

```
`r paste(knitr::knit(text = out), collapse = '\n')`




### Most significant deregulated pathway per topological measure
*Generates a heatmap of the most significant differentially active KEGG-pathways based on the top 100 deregulated genes.*

```{r annotdiff, fig.align='center', fig.height=7, fig.width=10,warning=FALSE,echo=F,eval=TRUE}
all_data <- readRDS(path)
for (i in names(all_data@annot)) {
  if (grepl('_x_', i) & grepl('ggi', i)) {
    paths <- read.csv(system.file("extdata", "selected_KEGG.csv", package = "CrossTalkeR"), header = F)
    filtered <- all_data@annot[[i]][grepl(paste(paths$V1, collapse = '|'), all_data@annot[[i]]$ID),]
    filtered <- filtered[filtered$p.adjust <= 0.05,]
    if (dim(filtered)[1] >= 2) {
      mat <- reshape2::acast(filtered, Description ~ type, value.var = "p.adjust")
      mat[is.na(mat)] = 1
      p1 <- Heatmap(-log10(mat), col = c('#FFFFFF', Blue2DarkOrange18Steps[11:18]), column_title = i, name = 'NES_pval')
      draw(p1)
    }
    else {
      print('Unable to do the enrichment')
    }
  }
}

```



## Genes Sankey Plot: Gene-based cell-cell interaction

```{r fig.align='center', fig.height=5, fig.width=10 ,message=FALSE, warning=FALSE, echo=FALSE,eval=TRUE }
all_data <- readRDS(path)
for (i in 1:length(names(all_data@tables))) {
  curr <- names(all_data@tables)[i]
  if (str_detect(curr, '_x_', negate = FALSE)) {
    for (gene in params$obj2) {
      print(params$obj2)
      p1 <- plot_sankey(all_data@tables[[curr]],
                        target = gene,
                        plt_name = paste0(curr, ' ', gene),tfflag=tfFlag)
    }
  }
}
```



```{r fig.align='center', fig.height=5, fig.width=10 ,message=FALSE, warning=FALSE, echo=F, eval = tfFlag}
asis_output("## Transcription Factor Sankey Plot: Transcription Factor-based intra cellular interactions\n")

all_data <- readRDS(path)
#if (!is.null(params$obj3)) {
  for (i in 1:length(names(all_data@rankings))) {
    curr_pagerank <- names(all_data@pca)[i]
    if (str_detect(curr_pagerank, '_x_', negate = FALSE) & str_detect(curr_pagerank, '_ggi', negate = FALSE)) {
      pagerank_table = all_data@rankings[[curr_pagerank]] %>%
        select(c("nodes", "Pagerank"))
      pagerank_table = as.data.frame(pagerank_table)
      rownames(pagerank_table) = pagerank_table$nodes
    } }

  for (i in 1:length(names(all_data@tables))) {
    curr <- names(all_data@tables)[i]
    if (str_detect(curr, '_x_', negate = FALSE)) {
      for (gene in params$obj3) {
        rtfl_table = all_data@tables[[curr]]
        suppressWarnings({
          plot_graph_sankey_tf(rtfl_table,
                               pagerank_table,
                               target = gene[[2]],
                               cluster = gene[[3]],
                               target_type = gene[[1]],
                               plt_name = paste0(curr, ' ', gene[[2]], ' ', gene[[3]]),
                               save_path = path)
        })
      }
    }
  }
#}
```



## LR analysis data

```{r fig.align='center', fig.height=5, fig.width=8,warning=FALSE,echo=F}
out <- c()
out1 <- list()
all_data <- readRDS(path)
for (i in 1:length(names(all_data@tables))) {
  curr <- names(all_data@tables)[i]
  if (str_detect(curr, '_x_', negate = FALSE)) {

    rmd_title <- paste0(curr, '_tbl')
    knit_expanded <- paste0("```{r results='", rmd_title, "', echo=FALSE, warning=FALSE}
                             \n\n                          datatable(all_data@tables[['", curr, "']][,c('Ligand.Cluster','Receptor.Cluster','Ligand','Receptor' ,'LRScore')],caption='", curr, "', extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) \n\n```")
    out <- c(out, knit_expanded)
    out1[[curr]] <- knit_expanded
  }
}

```

`r paste(knitr::knit(text = out), collapse = '\n')`