---
title: "Report diferential analysis"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
      toc: yes
      toc_depth: 3
      theme: simplex

params:
  obj1: "path to obj"
  thr: 'percentage edges to plot'

---

```{r message=FALSE, warning=FALSE, echo=FALSE, include=FALSE, echo=FALSE}
require(igraph)
require(dplyr)
require(tibble)
require(tidyr)
require(patchwork)
require(stringr)
require(CrossTalkeR)
require(ggraph)
require(graphlayouts)
require(pals)
require(factoextra)
require("DT")
require(ComplexHeatmap)
require(ggrepel)
require(extrafont)
extrafont::loadfonts()

```



### PCA GCI

*Here, a Principal Component Analysis (PCA) was done using the cell-gene interaction topological measures. High ranked observations $(>=2\sigma^{2})$ are labeled and each measure contribution is placed in the coordinate system.*

#### PC1 and PC2

```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
     curr <- names(all_data@pca)[i]
     if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){
      
     map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
     colnames(map_df) <- c("gene")
     map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
     })
     
     rmd_title <- paste0(curr,'_tbl')
     rmd_title1 <- paste0(curr,'_pca')
     x <- max(abs(all_data@pca[[curr]]$x[,1]))
     y <- max(abs(all_data@pca[[curr]]$x[,2]))
     z_x <- data@pca[[curr]]$x[,1]
     z_y <- data@pca[[curr]]$x[,2]
     ver_zx <- ifelse(abs(z_x)>=(2*data@pca[[curr]]$sdev[1]),1,0)
     ver_zy <- ifelse(abs(z_y)>=(2*data@pca[[curr]]$sdev[2]),1,0)
     print(fviz_pca_biplot(data@pca[[curr]],
                    axes = c(1,2),
                    pointshape = 20, pointsize = 2,labelsize = 10,
                    repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
                    geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(data@pca[[curr]]$x),NA)),size = 5)+
                    xlim(-x, x)+
                    ylim(-y, y)+
                    ggtitle(curr)+
                    theme(text = element_text(size = 7.5),
                          axis.title = element_text(size = 7.5),
                          axis.text = element_text(size = 7.5)))

   }  
}

```

#### PC2 and PC3

```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
     curr <- names(all_data@pca)[i]
     if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){
     
     map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
     colnames(map_df) <- c("gene")
     map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
     })
       
     rmd_title <- paste0(curr,'_tbl')
     rmd_title1 <- paste0(curr,'_pca')
     x <- max(abs(all_data@pca[[curr]]$x[,2]))
     y <- max(abs(all_data@pca[[curr]]$x[,3]))
     z_x <- data@pca[[curr]]$x[,2]
     z_y <- data@pca[[curr]]$x[,3]
     ver_zx <- ifelse(abs(z_x)>=(2*data@pca[[curr]]$sdev[2]),1,0)
     ver_zy <- ifelse(abs(z_y)>=(2*data@pca[[curr]]$sdev[3]),1,0)
     print(fviz_pca_biplot(data@pca[[curr]],
                    axes = c(2,3),
                    pointshape = 20, pointsize = 2,labelsize = 10,
                    repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
                    geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(data@pca[[curr]]$x),NA)),size = 5)+
                    xlim(-x, x)+
                    ylim(-y, y)+
                    ggtitle(curr)+
                    theme(text = element_text(size = 7.5),
                          axis.title = element_text(size = 7.5),
                          axis.text = element_text(size = 7.5)))

   }  
}

```

#### PC3 and PC4

```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
     curr <- names(all_data@pca)[i]
     if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){
       
     map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
     colnames(map_df) <- c("gene")
     map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
     })
       
     rmd_title <- paste0(curr,'_tbl')
     rmd_title1 <- paste0(curr,'_pca')
     x <- max(abs(all_data@pca[[curr]]$x[,3]))
     y <- max(abs(all_data@pca[[curr]]$x[,4]))
     z_x <- data@pca[[curr]]$x[,3]
     z_y <- data@pca[[curr]]$x[,4]
     ver_zx <- ifelse(abs(z_x)>=(2*data@pca[[curr]]$sdev[3]),1,0)
     ver_zy <- ifelse(abs(z_y)>=(2*data@pca[[curr]]$sdev[4]),1,0)
     print(fviz_pca_biplot(data@pca[[curr]],
                    axes = c(3,4),
                    pointshape = 20, pointsize = 2,labelsize = 10,
                    repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
                    geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(data@pca[[curr]]$x),NA)),size = 5)+
                    xlim(-x, x)+
                    ylim(-y, y)+
                    ggtitle(curr)+
                    theme(text = element_text(size = 7.5),
                          axis.title = element_text(size = 7.5),
                          axis.text = element_text(size = 7.5)))

   }  
}

```


#### PCA GCI Ligand and Receptor Genes PC1 and PC2


```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
  curr <- names(all_data@pca)[i]
  if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){

    pca_split = all_data@pca[[curr]]$x[,1]
    pca_split_names = names(pca_split)
    result_split_names = pca_split_names[grepl("|R", pca_split_names, fixed = TRUE) | grepl("|L", pca_split_names, fixed = TRUE)]
    col.num <- which(rownames(all_data@pca[[curr]]$x) %in% result_split_names)
    all_data@pca[[curr]]$x <- all_data@pca[[curr]]$x[sort(c(col.num)),]

    map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
    colnames(map_df) <- c("gene")
    map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
    })

    rmd_title <- paste0(curr,'_tbl')
    rmd_title1 <- paste0(curr,'_pca')
    x <- max(abs(all_data@pca[[curr]]$x[,1]))
    y <- max(abs(all_data@pca[[curr]]$x[,2]))
    z_x <- all_data@pca[[curr]]$x[,1]
    z_y <- all_data@pca[[curr]]$x[,2]
    ver_zx <- ifelse(abs(z_x)>=(2*all_data@pca[[curr]]$sdev[1]),1,0)
    ver_zy <- ifelse(abs(z_y)>=(2*all_data@pca[[curr]]$sdev[2]),1,0)
    print(fviz_pca_biplot(all_data@pca[[curr]],
                          axes = c(1,2),
                          pointshape = 20, pointsize = 2,labelsize = 10,
                          repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
            geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(all_data@pca[[curr]]$x),NA)),size = 5)+
            xlim(-x, x)+
            ylim(-y, y)+
            ggtitle(curr)+
            theme(text = element_text(size = 7.5),
                  axis.title = element_text(size = 7.5),
                  axis.text = element_text(size = 7.5)))

  }
}
```


#### PCA GCI Ligand and Receptor Genes PC2 and PC3


```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
  curr <- names(all_data@pca)[i]
  if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){

    pca_split = all_data@pca[[curr]]$x[,1]
    pca_split_names = names(pca_split)
    result_split_names = pca_split_names[grepl("|R", pca_split_names, fixed = TRUE) | grepl("|L", pca_split_names, fixed = TRUE)]
    col.num <- which(rownames(all_data@pca[[curr]]$x) %in% result_split_names)
    all_data@pca[[curr]]$x <- all_data@pca[[curr]]$x[sort(c(col.num)),]

    map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
    colnames(map_df) <- c("gene")
    map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
    })

    rmd_title <- paste0(curr,'_tbl')
    rmd_title1 <- paste0(curr,'_pca')
    x <- max(abs(all_data@pca[[curr]]$x[,2]))
    y <- max(abs(all_data@pca[[curr]]$x[,3]))
    z_x <- all_data@pca[[curr]]$x[,2]
    z_y <- all_data@pca[[curr]]$x[,3]
    ver_zx <- ifelse(abs(z_x)>=(2*all_data@pca[[curr]]$sdev[2]),1,0)
    ver_zy <- ifelse(abs(z_y)>=(2*all_data@pca[[curr]]$sdev[3]),1,0)
    print(fviz_pca_biplot(all_data@pca[[curr]],
                          axes = c(2,3),
                          pointshape = 20, pointsize = 2,labelsize = 10,
                          repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
            geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(all_data@pca[[curr]]$x),NA)),size = 5)+
            xlim(-x, x)+
            ylim(-y, y)+
            ggtitle(curr)+
            theme(text = element_text(size = 7.5),
                  axis.title = element_text(size = 7.5),
                  axis.text = element_text(size = 7.5)))

  }
}
```


#### PCA GCI Ligand and Receptor Genes PC3 and PC4


```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
  curr <- names(all_data@pca)[i]
  if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){

    pca_split = all_data@pca[[curr]]$x[,1]
    pca_split_names = names(pca_split)
    result_split_names = pca_split_names[grepl("|R", pca_split_names, fixed = TRUE) | grepl("|L", pca_split_names, fixed = TRUE)]
    col.num <- which(rownames(all_data@pca[[curr]]$x) %in% result_split_names)
    all_data@pca[[curr]]$x <- all_data@pca[[curr]]$x[sort(c(col.num)),]

    map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
    colnames(map_df) <- c("gene")
    map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
    })

    rmd_title <- paste0(curr,'_tbl')
    rmd_title1 <- paste0(curr,'_pca')
    x <- max(abs(all_data@pca[[curr]]$x[,3]))
    y <- max(abs(all_data@pca[[curr]]$x[,4]))
    z_x <- all_data@pca[[curr]]$x[,3]
    z_y <- all_data@pca[[curr]]$x[,4]
    ver_zx <- ifelse(abs(z_x)>=(2*all_data@pca[[curr]]$sdev[3]),1,0)
    ver_zy <- ifelse(abs(z_y)>=(2*all_data@pca[[curr]]$sdev[4]),1,0)
    print(fviz_pca_biplot(all_data@pca[[curr]],
                          axes = c(3,4),
                          pointshape = 20, pointsize = 2,labelsize = 10,
                          repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
            geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(all_data@pca[[curr]]$x),NA)),size = 5)+
            xlim(-x, x)+
            ylim(-y, y)+
            ggtitle(curr)+
            theme(text = element_text(size = 7.5),
                  axis.title = element_text(size = 7.5),
                  axis.text = element_text(size = 7.5)))

  }
}
```


#### PCA GCI Transcription Factor Genes PC1 and PC2


```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
  curr <- names(all_data@pca)[i]
  if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){

    pca_split = all_data@pca[[curr]]$x[,1]
    pca_split_names = names(pca_split)
    result_split_names = pca_split_names[grepl("|TF", pca_split_names, fixed = TRUE)]
    col.num <- which(rownames(all_data@pca[[curr]]$x) %in% result_split_names)
    all_data@pca[[curr]]$x <- all_data@pca[[curr]]$x[sort(c(col.num)),]

    map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
    colnames(map_df) <- c("gene")
    map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
    })

    rmd_title <- paste0(curr,'_tbl')
    rmd_title1 <- paste0(curr,'_pca')
    x <- max(abs(all_data@pca[[curr]]$x[,1]))
    y <- max(abs(all_data@pca[[curr]]$x[,2]))
    z_x <- all_data@pca[[curr]]$x[,1]
    z_y <- all_data@pca[[curr]]$x[,2]
    ver_zx <- ifelse(abs(z_x)>=(2*all_data@pca[[curr]]$sdev[1]),1,0)
    ver_zy <- ifelse(abs(z_y)>=(2*all_data@pca[[curr]]$sdev[2]),1,0)
    print(fviz_pca_biplot(all_data@pca[[curr]],
                          axes = c(1,2),
                          pointshape = 20, pointsize = 2,labelsize = 10,
                          repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
            geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(all_data@pca[[curr]]$x),NA)),size = 5)+
            xlim(-x, x)+
            ylim(-y, y)+
            ggtitle(curr)+
            theme(text = element_text(size = 7.5),
                  axis.title = element_text(size = 7.5),
                  axis.text = element_text(size = 7.5)))

  }
}
```


#### PCA GCI Transcription Factor Genes PC2 and PC3


```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
  curr <- names(all_data@pca)[i]
  if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){

    pca_split = all_data@pca[[curr]]$x[,1]
    pca_split_names = names(pca_split)
    result_split_names = pca_split_names[grepl("|TF", pca_split_names, fixed = TRUE)]
    col.num <- which(rownames(all_data@pca[[curr]]$x) %in% result_split_names)
    all_data@pca[[curr]]$x <- all_data@pca[[curr]]$x[sort(c(col.num)),]

    map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
    colnames(map_df) <- c("gene")
    map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
    })

    rmd_title <- paste0(curr,'_tbl')
    rmd_title1 <- paste0(curr,'_pca')
    x <- max(abs(all_data@pca[[curr]]$x[,2]))
    y <- max(abs(all_data@pca[[curr]]$x[,3]))
    z_x <- all_data@pca[[curr]]$x[,2]
    z_y <- all_data@pca[[curr]]$x[,3]
    ver_zx <- ifelse(abs(z_x)>=(2*all_data@pca[[curr]]$sdev[2]),1,0)
    ver_zy <- ifelse(abs(z_y)>=(2*all_data@pca[[curr]]$sdev[3]),1,0)
    print(fviz_pca_biplot(all_data@pca[[curr]],
                          axes = c(2,3),
                          pointshape = 20, pointsize = 2,labelsize = 10,
                          repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
            geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(all_data@pca[[curr]]$x),NA)),size = 5)+
            xlim(-x, x)+
            ylim(-y, y)+
            ggtitle(curr)+
            theme(text = element_text(size = 7.5),
                  axis.title = element_text(size = 7.5),
                  axis.text = element_text(size = 7.5)))

  }
}
```


#### PCA GCI Transcription Factor Genes PC3 and PC4


```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
  curr <- names(all_data@pca)[i]
  if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){

    pca_split = all_data@pca[[curr]]$x[,1]
    pca_split_names = names(pca_split)
    result_split_names = pca_split_names[grepl("|TF", pca_split_names, fixed = TRUE)]
    col.num <- which(rownames(all_data@pca[[curr]]$x) %in% result_split_names)
    all_data@pca[[curr]]$x <- all_data@pca[[curr]]$x[sort(c(col.num)),]

    map_df <- as.data.frame(rownames(all_data@pca[[curr]]$x))
    colnames(map_df) <- c("gene")
    map_df$mapping <- sapply(map_df$gene, function(gene) {
      if (grepl("|R", gene, fixed = TRUE)) {
        txt <- "Receptor"
      } else if (grepl("|L", gene, fixed = TRUE)) {
        txt <- "Ligand"
      } else {
        txt <- "Transcription Factor"
      }
      return(txt)
    })

    rmd_title <- paste0(curr,'_tbl')
    rmd_title1 <- paste0(curr,'_pca')
    x <- max(abs(all_data@pca[[curr]]$x[,3]))
    y <- max(abs(all_data@pca[[curr]]$x[,4]))
    z_x <- all_data@pca[[curr]]$x[,3]
    z_y <- all_data@pca[[curr]]$x[,4]
    ver_zx <- ifelse(abs(z_x)>=(2*all_data@pca[[curr]]$sdev[3]),1,0)
    ver_zy <- ifelse(abs(z_y)>=(2*all_data@pca[[curr]]$sdev[4]),1,0)
    print(fviz_pca_biplot(all_data@pca[[curr]],
                          axes = c(3,4),
                          pointshape = 20, pointsize = 2,labelsize = 10,
                          repel = FALSE,max.overlaps=100,label='var', habillage = map_df$mapping)+
            geom_label_repel(aes(label=ifelse((ver_zx | ver_zy),rownames(all_data@pca[[curr]]$x),NA)),size = 5)+
            xlim(-x, x)+
            ylim(-y, y)+
            ggtitle(curr)+
            theme(text = element_text(size = 7.5),
                  axis.title = element_text(size = 7.5),
                  axis.text = element_text(size = 7.5)))

  }
}
```


### Pagerank Log Ratio


```{r fig.align='center',warning=FALSE,echo=FALSE}
all_data <- readRDS(path)
for(i in 2:length(names(all_data@rankings))){
  curr <- names(all_data@rankings)[i]
  if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, 'ggi', negate = FALSE)){
    tmp <- top_n(all_data@rankings[[curr]],20,abs(.data$Pagerank))
    signal <- ifelse(tmp$Pagerank < 0, 'negative','positive')
    print(ggplot(tmp, aes(x=Pagerank,y=reorder(nodes,Pagerank),fill=signal))+
        geom_bar(stat="identity")+
        scale_fill_manual(values = c(Blue2DarkOrange18Steps[4],Blue2DarkOrange18Steps[14]))+
        theme_minimal())
  }  
}
```





### PCA GCI Table

```{r fig.align='center',warning=FALSE,echo=FALSE}
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
     curr <- names(all_data@pca)[i]
     if(str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){
     rmd_title <- paste0(curr,'_tbl')
     rmd_title1 <- paste0(curr,'_pca')
     title <- paste0('\n\n#### Table PCA CGI ',curr)
     knit_expanded <- paste0("```{r , results='",rmd_title,"', echo=FALSE, warning=FALSE}\n\n
         pca <- all_data@pca[['",curr,"']]$x[,1:2]
         pca[,1] <- round(pca[,1],6)
         pca[,2] <- round(pca[,2],6)
         ranking <- cbind(all_data@rankings[['",curr,"']][,2:dim(all_data@rankings[['",curr,"']])[2]],pca[all_data@rankings[['",curr,"']]$nodes,])
         datatable(ranking,
                 caption='",curr,"',
                 extensions = 'Buttons',
                 options = list(dom = 'Bfrtip',
                                buttons = c('copy',
                                            'csv',
                                            'excel',
                                            'pdf', 'print'),
                               autoWidth = FALSE
                               )
                )

     ```")
     out <- c(out,knit_expanded)
     out1[[curr]] <-knit_expanded
   }  
}

```
`r paste(knitr::knit(text = out), collapse = '\n')`




### Most significant deregulated pathway per topological measure
*Generates a heatmap of the most significant differentially active KEGG-pathways based on the top 100 deregulated genes.*

```{r annotdiff, fig.align='center', fig.height=7, fig.width=10,warning=FALSE,echo=F}
all_data <- readRDS(path)
for(i in names(all_data@annot)){
  if( grepl('_x_',i) & grepl('ggi',i) ){
    paths <- read.csv(system.file("extdata","selected_KEGG.csv",package = "CrossTalkeR"),header=F)
    filtered <- all_data@annot[[i]][grepl(paste(paths$V1,collapse='|'), all_data@annot[[i]]$ID),]
    filtered <- filtered[filtered$p.adjust<=0.05,]
    if(dim(filtered)[1] >=2){
    mat <- reshape2::acast(filtered, Description ~ type, value.var = "p.adjust")
    mat[is.na(mat)]=1
    p1<-Heatmap(-log10(mat), col =c('#FFFFFF',Blue2DarkOrange18Steps[11:18]), column_title =i,name='-log10(p.adjust)')
    draw(p1)
   }
   else{
     print('Unnable to do the enrichment')
   }  
  }
}

```



## Genes Sankey Plot: Gene-based cell-cell interaction


```{r fig.align='center', fig.height=5, fig.width=10 ,message=FALSE, warning=FALSE, echo=F}
all_data <- readRDS(path)
for(i in 1:length(names(all_data@tables))){
  curr <- names(all_data@tables)[i]
  if(str_detect(curr, '_x_', negate = FALSE)){
      for(gene in params$obj2){
        suppressWarnings({plot_sankey(all_data@tables[[curr]],
                    target=gene,plt_name=paste0(curr,' ',gene))})
      }
  }
}
```



## Transkription Factor Sankey Plot: Transcription Factor-based intra cellular interactions


```{r fig.align='center', fig.height=5, fig.width=10 ,message=FALSE, warning=FALSE, echo=F}
all_data <- readRDS(path)

for(i in 1:length(names(all_data@rankings))){
  curr_pagerank <- names(all_data@pca)[i]
  if(str_detect(curr_pagerank, '_x_', negate = FALSE) & str_detect(curr_pagerank, '_ggi', negate = FALSE)){
    pagerank_table = all_data@rankings[[curr_pagerank]] %>%
      select(c("nodes", "Pagerank"))
  }}

for (i in 1:length(names(all_data@tables))) {
  curr <- names(all_data@tables)[i]
  if (str_detect(curr, '_x_', negate = FALSE)) {
    for (gene in params$obj3) {
      table_rtfs = all_data@tables[[curr]] %>%
        filter(type_gene_B == "Transcription Factor") %>%
        subset(
          select = c(
            "Ligand",
            "Receptor",
            "LRScore",
            "type_gene_A",
            "type_gene_B",
            "Ligand.Cluster"
          )
        ) %>%
        rename(
          Receptor = Ligand,
          TF = Receptor,
          Cluster = Ligand.Cluster,
          TFScore = LRScore
        )
      
      table_tfl = all_data@tables[[curr]] %>%
        filter(type_gene_A == "Transcription Factor") %>%
        subset(
          select = c(
            "Ligand",
            "Receptor",
            "LRScore",
            "type_gene_A",
            "type_gene_B",
            "Ligand.Cluster"
          )
        ) %>%
        rename(
          Ligand = Receptor,
          TF = Ligand,
          Cluster = Ligand.Cluster,
          TFScore = LRScore
        )
      
      df_combined = left_join(table_rtfs, table_tfl, by = "TF", all = TRUE) %>%
        na.omit()
      suppressWarnings({
        plot_sankey_tf_pagerank(df_combined,
                    pagerank_table,
                    target = gene[[2]],
                    cluster = gene[[3]],
                    target_type = gene[[1]],
                    plt_name = paste0(curr, ' ', gene[[2]]))
      })
    }
  }
}
```



## LR analysis data

```{r fig.align='center', fig.height=5, fig.width=8,warning=FALSE,echo=F}
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@tables))){
     curr <- names(all_data@tables)[i]
     if(str_detect(curr, '_x_', negate = FALSE)){

     rmd_title <- paste0(curr,'_tbl')
     knit_expanded <- paste0("```{r results='",rmd_title,"', echo=FALSE, warning=FALSE}
                             \n\n                          datatable(all_data@tables[['",curr,"']][,c('Ligand.Cluster','Receptor.Cluster','Ligand','Receptor' ,'LRScore')],caption='",curr,"', extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) \n\n```")
     out <- c(out,knit_expanded)
     out1[[curr]] <-knit_expanded
   }
}

```

`r paste(knitr::knit(text = out), collapse = '\n')`
