---
title: "Report per condition"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
html_document:
toc: yes
toc_depth: 3
theme: simplex
params:
obj1: "path to obj"
thr: 'cutoff'
selcln: 'columns'
---

```{r message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
require(igraph)
require(dplyr)
require(tibble)
require(tidyr)
require(stringr)
require(patchwork)
require(CrossTalkeR)
require(factoextra)
require(ComplexHeatmap)
require("DT")
require(ggrepel)


all_data <- readRDS(params$obj1)
PCA_TF_flag <- FALSE
for (name in names(all_data@tables)) {
  if (!str_detect(name, '_x_', negate = FALSE)) {
    if (("Transcription Factor" %in% all_data@tables[[name]]$type_gene_A) | ("Transcription Factor" %in% all_data@tables[[name]]$type_gene_B)) {
      PCA_TF_flag <- TRUE
    }
  }
}

```


### PCA GCI Table

```{r fig.align='center',warning=FALSE,echo=FALSE}
out <- c()
out1 <- list()
all_data <- readRDS(path)
for (i in 1:length(names(all_data@pca))) {
  curr <- names(all_data@pca)[i]
  if (!str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)) {
    rmd_title <- paste0(curr, '_tbl')
    rmd_title1 <- paste0(curr, '_pca')
    title <- paste0('\n\n#### Table PCA CGI ', curr)
    knit_expanded <- paste0("```{r , results='", rmd_title, "', echo=FALSE, warning=FALSE}\n\n
         pca <- all_data@pca[['", curr, "']]$x[,1:2]
         pca[,1] <- round(pca[,1],6)
         pca[,2] <- round(pca[,2],6)
         ranking <- cbind(all_data@rankings[['", curr, "']][,2:dim(all_data@rankings[['", curr, "']])[2]],pca[all_data@rankings[['", curr, "']]$nodes,])
         datatable(ranking,
                 caption='", curr, "',
                 extensions = 'Buttons',
                 options = list(dom = 'Bfrtip',
                                buttons = c('copy',
                                            'csv',
                                            'excel',
                                            'pdf', 'print'),
                               autoWidth = FALSE
                             ))\n\n```")
    out <- c(out, knit_expanded)
    out1[[curr]] <- knit_expanded
  }
}
```

`r paste(knitr::knit(text = out), collapse = '\n')`

### Most significant deregulated pathway per topological measure

*Generates a heatmap of the most significant differentially active KEGG-pathways based on the top 100 deregulated genes*


```{r annotsingle, fig.align='center', fig.height=7,fig.width=9,warning=FALSE,echo=F,eval=T}
out <- c()
out1 <- list()
plots <- list()
all_data <- readRDS(path)
paths <- read.csv(system.file("extdata", "selected_KEGG.csv", package = "CrossTalkeR"), header = T)
for (i in names(all_data@annot)) {
  if (str_detect(i, 'ggi', negate = FALSE) & !str_detect(i, '_x_', negate = FALSE)) {
    out <- tryCatch({
      filtered <- all_data@annot[[i]][grepl(paste(paths$V1, collapse = '|'), all_data@annot[[i]]$ID),]
      filtered <- filtered[filtered$p.adjust <= 0.05,]
      if (sum(str_detect(filtered$Description, 'house mouse')) > 0) {
        filtered$Description <- substr(filtered$Description, 1, nchar(filtered$Description) - 29)
      }
      mat <- reshape2::acast(filtered, Description ~ type, value.var = "p.adjust")
      mat[is.na(mat)] = 1
      p1 <- Heatmap(-log10(mat), col = c('#FFFFFF', Blue2DarkOrange18Steps[11:18]), column_title = i, name = '-log10(p.adjust)')
      draw(p1)
    },
      error = function(cond) {
        message("Significant enrichment not found")
      })
  }
}
```

## LR analysis data

```{r fig.align='center', fig.height=5, fig.width=8,warning=FALSE,echo=F}
out <- c()
out1 <- list()
for (i in 1:length(names(all_data@tables))) {
  curr <- names(all_data@tables)[i]
  if (!str_detect(curr, '_x_', negate = FALSE)) {
    rmd_title <- paste0(curr, '_tbl')
    knit_expanded <- paste0("```{r results='", rmd_title, "', echo=FALSE,warning=F}
                                 \n\n                          datatable(all_data@tables[['", curr, "']][,c('source','target','gene_A','gene_B' ,'LRScore')],caption='", curr, "', extensions = 'Buttons', options = list(
        dom = 'Bfrtip',
        buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) \n\n```")
    out <- c(out, knit_expanded)
    out1[[curr]] <- knit_expanded
  }
}
```

`r paste(knitr::knit(text = out), collapse = '\n')`