---
title: "Report per condition"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
      toc: yes
      toc_depth: 3
      theme: simplex
params:
  obj1: "path to obj"
  thr: 'cutoff'
  selcln: 'columns'
---

```{r message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
require(igraph)
require(dplyr)
require(tibble)
require(tidyr)
require(stringr)
require(patchwork)
require(CrossTalkeR)
require(factoextra)
require(ComplexHeatmap)
require("DT")
require(ggrepel)

```


### PCA CGI

*Here, a Principal Component Analysis (PCA) was done using the cell-gene interaction topological measures.High ranked observations (>=2$\sigma^{2}$) are labeled and each measure contribution is placed in the coordinate system*

```{r fig.align='center',warning=FALSE,echo=FALSE,fig.width=12,fig.height=12}
path <-params$obj1
all_data <- readRDS(path)
out <- c()
out1 <- list()
for(i in 1:length(names(all_data@pca))){
     curr <- names(all_data@pca)[i]
     if(!str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){
     rmd_title <- paste0(curr,'_tbl')
     rmd_title1 <- paste0(curr,'_pca')
     x <- max(abs(all_data@pca[[curr]]$x[,1]))
     y <- max(abs(all_data@pca[[curr]]$x[,2]))
     z_x <- data@pca[[curr]]$x[,1]
     z_y <- data@pca[[curr]]$x[,2]
     ver_zx <- ifelse(abs(z_x)>2*data@pca[[curr]]$sdev[1],1,0)
     ver_zy <- ifelse(abs(z_y)>2*data@pca[[curr]]$sdev[2],1,0)
     print(fviz_pca_biplot(data@pca[[curr]],
                    axes = c(1,2),
                    pointshape = 21, pointsize = 0.5,labelsize = 12,
                    repel = TRUE,max.overlaps=100,label='var')+
                    geom_label_repel(aes(label=ifelse(ver_zx & ver_zy,rownames(data@pca[[curr]]$x),NA)),hjust=0, vjust=0,size = 7)+
                    xlim(-x, x)+
                    ylim(-y, y)+
                    ggtitle(curr)+
                    theme(text = element_text(size = 7.5),
                          axis.title = element_text(size = 7.5),
                          axis.text = element_text(size = 7.5)))
   }  
}
```


### PCA GCI Table

```{r fig.align='center',warning=FALSE,echo=FALSE}
out <- c()
out1 <- list()
all_data <- readRDS(path)
for(i in 1:length(names(all_data@pca))){
     curr <- names(all_data@pca)[i]
     if(!str_detect(curr, '_x_', negate = FALSE) & str_detect(curr, '_ggi', negate = FALSE)){
     rmd_title <- paste0(curr,'_tbl')
     rmd_title1 <- paste0(curr,'_pca')
     title <- paste0('\n\n#### Table PCA CGI ',curr)
     knit_expanded <- paste0("```{r , results='",rmd_title,"', echo=FALSE, warning=FALSE}\n\n
         pca <- all_data@pca[['",curr,"']]$x[,1:2]
         pca[,1] <- round(pca[,1],6)
         pca[,2] <- round(pca[,2],6)
         ranking <- cbind(all_data@rankings[['",curr,"']][,2:dim(all_data@rankings[['",curr,"']])[2]],pca[all_data@rankings[['",curr,"']]$nodes,])
         datatable(ranking,
                 caption='",curr,"',
                 extensions = 'Buttons',
                 options = list(dom = 'Bfrtip',
                                buttons = c('copy',
                                            'csv',
                                            'excel',
                                            'pdf', 'print'),
                               autoWidth = FALSE
                               )
                )

     ```")
     out <- c(out,knit_expanded)
     out1[[curr]] <-knit_expanded
   }  
}

```
`r paste(knitr::knit(text = out), collapse = '\n')`

### Most significant deregulated pathway per topological measure

*Generates a heatmap of the most significant differentially active KEGG-pathways based on the top 100 deregulated genes*


```{r annotsingle, fig.align='center', fig.height=7,fig.width=10,warning=FALSE,echo=F,eval=T}
out <- c()
out1 <- list()
plots <- list()
all_data <- readRDS(path)
paths <- read.csv(system.file("extdata","selected_KEGG.csv",package = "CrossTalkeR"),header=T)
for(i in names(all_data@annot)){
  if(str_detect(i, 'ggi', negate = FALSE) & !str_detect(i, '_x_', negate = FALSE)){
     out <- tryCatch({
            filtered <- all_data@annot[[i]][grepl(paste(paths$V1,collapse='|'), all_data@annot[[i]]$ID),]
            filtered <- filtered[filtered$p.adjust<=0.05,]
            mat <- reshape2::acast(filtered, Description ~ type, value.var = "p.adjust")
            mat[is.na(mat)]=1
            p1<-Heatmap(-log10(mat), col = c('#FFFFFF',Blue2DarkOrange18Steps[11:18]), column_title =i,name='-log10(p.adjust)')
            draw(p1)
            },
        error=function(cond){
            message("Significant enrichment not found")
        })    
  }
}
```

## LR analysis data

```{r fig.align='center', fig.height=5, fig.width=8,warning=FALSE,echo=F}
out <- c()
out1 <- list()
for(i in 1:length(names(all_data@tables))){
     curr <- names(all_data@tables)[i]
     if(!str_detect(curr, '_x_', negate = FALSE)){
         rmd_title <- paste0(curr,'_tbl')
         knit_expanded <- paste0("```{r results='",rmd_title,"', echo=FALSE,warning=F}
                                 \n\n                          datatable(all_data@tables[['",curr,"']][,c('Ligand.Cluster','Receptor.Cluster','Ligand','Receptor' ,'LRScore')],caption='",curr,"', extensions = 'Buttons', options = list(
        dom = 'Bfrtip',
        buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) \n\n```")
         out <- c(out,knit_expanded)
         out1[[curr]] <-knit_expanded
     }
}

```

`r paste(knitr::knit(text = out), collapse = '\n')`
